### 2015-09-29 untitled.tex
edited untitled.tex

>>>>

Therefore, the above example shows that there exists (at least) a sporadic segmented self-suspending task system that is schedulable under fixed-priority scheduling without any enforcement, but the corresponding schedule by using period enforcer algorithm is not feasible. In this example, it is also clear that we can pessimistically convert the two computation segments of task $\tau_2$ into two deferrable tasks $\tau_2^1$ and $\tau_2^2$. The deferrable time of task $\tau_2^1$ is $0$, whereas the deferrable time of task $\tau_2^2$ is at most \emph{$9$}. With the above conversion, we can clearly see that the deferrable task set $\{\tau_1, \tau_2^1, \tau_2^2\}$ is in fact not schedulable by the rate-monotonic priority assignment since we can release a job of $\tau_1$ together with a job of $\tau_2^2$ (after its worst-case deferrable time).
